%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Corporate Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {AI-powered Story Bot} % Project name
    {Full Stack Development} % Role
    {} % Location
    {May 2024 - Jul. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Participated in the full stack development of an AI-powered story bot using Claude’s API for personalized stories.}
        \item {Used technologies such as Python, Flask, React, AWS, and Claude.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {PayMe from HSBC} % Project name
    {Backend Development} % Role
    {} % Location
    {Nov. 2022 - Jul. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Participated in the backend development of the Auto Top Up feature and cloud migration.}
        \item {Used technologies such as Java, Spring Cloud, Azure, and AWS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DBS Digibank CN} % Project name
    {Backend Development} % Role
    {} % Location
    {Jul. 2022 - Nov. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Participated in the backend development of mutual funds microservices.}
        \item {Used technologies such as Java, Spring Cloud, and Pivotal Cloud Foundry.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DBS Client Connect} % Project name
    {Backend Development} % Role
    {} % Location
    {Dec. 2021 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Participated in the backend development of equity trading microservices.}
        \item {Used technologies such as Java, Spring Cloud, and Pivotal Cloud Foundry.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ShowMeBug} % Project name
    {Platform Integration} % Role
    {} % Location
    {Jul. 2021 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Responsible for the integration between the platform and Enterprise WeChat, including login and easy interview entrance.}
        \item {Used technologies such as Ruby on Rails, PostgreSQL, and WeChat SDK.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Square Root Inc Projects} % Project name
    {Multiple Roles: Team Management, Development} % Role
    {} % Location
    {Jan. 2018 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Participated in 50 miscellaneous projects including websites, games, apps, and WeChat mini programs.}
        \item {Responsibilities included team management, contract negotiation, project management, client communications, and software development.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Super Brain TV Program WeChat Mini Program} % Project name
    {Backend and Frontend Development} % Role
    {} % Location
    {Feb. 2018 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Responsible for the backend and frontend development of the WeChat Mini Program for the TV show.}
        \item {Used technologies such as Java, Spring, JavaScript, HTML, and AliCloud.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Chongding Conference} % Project name
    {Backend and Frontend Development} % Role
    {} % Location
    {Sep. 2017 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Responsible for backend development and admin panel frontend development for a live-streaming trivia app.}
        \item {Used technologies such as Java, Spring, WebSocket, and Netty.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mianbao Live} % Project name
    {Backend Refactoring} % Role
    {} % Location
    {Sep. 2017 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Responsible for refactoring the backend of a one-stop content monetization platform.}
        \item {Used technologies such as PHP, TypeScript, Laravel, and Go.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fun Live} % Project name
    {Full Stack Development} % Role
    {} % Location
    {Jun. 2016 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Responsible for most code development of a knowledge live broadcast platform.}
        \item {Used technologies such as PHP, JavaScript, HTML, AliCloud, and RTMP Streaming.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {LeanCloud SDK and LeanChat} % Project name
    {SDK and App Development} % Role
    {} % Location
    {Jul. 2014 - Oct. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Responsible for development of Objective-C and Java SDKs, and all development of their demo app LeanChat.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
