%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Papers}

\begin{cvparagraph}
  I'm a self-taught researcher with three academic-style papers on reversing myopia and natural vision restoration, inspired by the works of Yin Wang and Todd Becker, supported by three years of experimentation. In computer science, I am still striving to make similar breakthroughs.
\end{cvparagraph}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Experimental Verification of the Natural Vision Restoration Method} % Paper title
    {Li, Zhiwei} % Author
    {Zhiwei’s Blog} % Published in
    {Jun. 2023} % Date
    {
      \begin{cvitems}
        \item {Discussed experiments validating a natural vision restoration method.}
        \item {Published online: \href{http://lzwjava.github.io/vision-restoration-en}{http://lzwjava.github.io/vision-restoration-en}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {The Discussion Regarding Astigmatism When the Eyeballs Reverse to the Normal Shape} % Paper title
    {Li, Zhiwei} % Author
    {Zhiwei’s Blog} % Published in
    {Jun. 2023} % Date
    {
      \begin{cvitems}
        \item {Analyzed the relationship between astigmatism and the reversal of eyeball shape to normal.}
        \item {Published online: \href{https://lzwjava.github.io/astigmatism-en}{https://lzwjava.github.io/astigmatism-en}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Natural Vision Restoration: The Principle of ‘Just Barely Clear’} % Paper title
    {Li, Zhiwei} % Author
    {Zhiwei’s Blog} % Published in
    {Nov. 2024} % Date
    {
      \begin{cvitems}
        \item {Explored the concept of “just barely clear” as a guiding principle for natural vision restoration.}
        \item {Published online: \href{https://lzwjava.github.io/barely-clear-en}{https://lzwjava.github.io/barely-clear-en}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
