%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Personal Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Algorithm Solutions} % Project name
    {Open Source Contributions} % Role
    {} % Location
    {2013 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Solutions to algorithm problems, hosted on GitHub with 2466 commits.}
        \item {Implemented primarily in Java.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Personal Blog} % Project name
    {Blog Development} % Role
    {} % Location
    {2013 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Maintained a bilingual blog (English and Chinese) with 500 commits.}
        \item {Shared insights on programming, technology, and personal development.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Live Server} % Project name
    {Backend Development} % Role
    {} % Location
    {2016 - 2017} % Date(s)
    {
      \begin{cvitems}
        \item {Backend development of a knowledge live broadcast platform.}
        \item {Used technologies such as PHP with 660 commits.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Live Mobile Web} % Project name
    {Frontend Development} % Role
    {} % Location
    {2016 - 2017} % Date(s)
    {
      \begin{cvitems}
        \item {Developed the mobile frontend of a knowledge live broadcast platform.}
        \item {Utilized Vue and JavaScript with 528 commits.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Live Web} % Project name
    {Frontend Development} % Role
    {} % Location
    {2016 - 2017} % Date(s)
    {
      \begin{cvitems}
        \item {Developed the desktop frontend of a knowledge live broadcast platform.}
        \item {Used Vue with 140 commits.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Live WeChat Mini Program} % Project name
    {Frontend Development} % Role
    {} % Location
    {2016 - 2017} % Date(s)
    {
      \begin{cvitems}
        \item {Developed the WeChat Mini Program for a knowledge live broadcast platform.}
        \item {Implemented in JavaScript with 63 commits.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Code Review Server} % Project name
    {Backend Development} % Role
    {} % Location
    {2015 - 2016} % Date(s)
    {
      \begin{cvitems}
        \item {Developed the backend for a professional platform for code review.}
        \item {Utilized PHP with 275 commits.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Code Review Web} % Project name
    {Frontend Development} % Role
    {} % Location
    {2015 - 2016} % Date(s)
    {
      \begin{cvitems}
        \item {Developed the frontend for a professional platform for code review.}
        \item {Utilized Vue and JavaScript with 302 commits.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {LeanChat iOS} % Project name
    {Mobile App Development} % Role
    {} % Location
    {2014 - 2015} % Date(s)
    {
      \begin{cvitems}
        \item {Developed an iOS chat application demonstrating LeanCloud SDK.}
        \item {Implemented in Objective-C with 556 commits.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {LeanChat Android} % Project name
    {Mobile App Development} % Role
    {} % Location
    {2014 - 2015} % Date(s)
    {
      \begin{cvitems}
        \item {Developed an Android chat application demonstrating LeanCloud SDK.}
        \item {Implemented in Java with 412 commits.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Feynman Lectures Mobi} % Project name
    {Tool Development} % Role
    {} % Location
    {2020 - 2021} % Date(s)
    {
      \begin{cvitems}
        \item {Developed a tool to convert LaTeX to SVG for creating mobi ebooks.}
        \item {Implemented in Python with 47 commits.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
