%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cvparagraph}
    \textbullet\ 29-year-old male, Chinese citizen, resides in Guangzhou. \\
    \textbullet\ Achieved top 300 in Guangdong NOIP 2011 and solved around 1000 algorithm problems online. \\
    \textbullet\ Studied for one year at Beijing Forestry University before dropping out. Pursuing an associate degree through self-taught education, with seven courses completed. \\
    \textbullet\ Worked primarily at LeanCloud, Beijing Square Root, Beyondsoft (outsourced to DBS Bank), and Farben Information (outsourced to HSBC Bank). \\
    \textbullet\ Accumulated 10 years of professional experience, including 7 years in corporate roles and 3 years as a freelancer. \\
    \textbullet\ Specializes in 2 years of mobile engineering (Android, iOS), 7 years of full-stack engineering (6 years backend, 1 year frontend), and 1 year in machine learning/big data. \\
    \textbullet\ Proficient in Java, Spring, Spring Boot, MySQL, Redis, APIs, networking, containers, and distributed systems. Strong understanding of HTML, CSS, Browser APIs, JavaScript, Vue.js, React, Angular, and iOS/Android development. \\
    \textbullet\ Familiar with logging, database, and microservice modules on Alibaba Cloud, AWS, and Azure. \\
    \textbullet\ Native in Chinese, proficient in English (IELTS 6). \\
    \textbullet\ Read over 320 books spanning textbooks, personal development, business, technology, and history. \\
    \textbullet\ Developed 10 open-source GitHub projects as a main developer, each with over 500 commits. Available at \href{https://github.com/lzwjava}{https://github.com/lzwjava}. \\
    \textbullet\ Self-taught researcher with three academic-style papers on reversing myopia and natural vision restoration, inspired by the works of Yin Wang and Todd Becker, backed by three years of experimentation. \\
    \textbullet\ Detailed software portfolio available at \href{https://lzwjava.github.io/pages/portfolio}{https://lzwjava.github.io/pages/portfolio}.
    \end{cvparagraph}

    
